<header style="text-align: center">

### 2019-05-24 report/report.Rmd
Loop to multiple figs from array

```{r, fig.align='center', fig.height=2.5}
ddr.times(data$real$flights, nearby[1], event, group = 'nearby')
ddr.times(data$real$flights, nearby[1], event, group = 'nearby')
ddr.times(data$real$flights, nearby[2], event, group = 'nearby')
ddr.times(data$real$flights, nearby[4], event, group = 'nearby')
ddr.times(data$real$flights, nearby[5], event, group = 'nearby')
```

>>>>

```{r, fig.align='center'}
htmltools::tagList(lapply(nearby, function(airport) {
	ddr.times(data$real$flights, airport, event, group = 'nearby', height = '250px')
}))
```
